---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# iso.week.half

<!-- badges: start -->
<!-- badges: end -->

The goal of iso.week.half is to obtain a week number for a date, with an additional 0.5 for a date on Tuesday, Wednesday or Thursday.

## Installation

From Github:

``` r
devtools::install_github("nxskok/iso.week.half")
```

## Example

```{r example}
library(iso.week.half)
iso_week_half(as.Date("2020-07-03"))
iso_week_half(as.Date("2020-07-02"))
```

in 2020, July 2 was in a different half-week because it was on a Thursday.

## `base_year`

By default, the base year is 2020. If you have dates from other years, the week numbers will look funny. Set the base year accordingly if that bothers you:

```{r}
iso_week_half(as.Date("2019-07-03"))
iso_week_half(as.Date("2021-07-02"))
```

and then

```{r}
iso_week_half(as.Date("2019-07-03"), 2019)
iso_week_half(as.Date("2021-07-02"), 2021)
```

The advantage to doing it this way is that the week numbers from different years will order properly:

```{r}
iso_week_half(as.Date("2017-09-03"), 2019)
iso_week_half(as.Date("2018-07-02"), 2021)
iso_week_half(as.Date("2019-05-03"), 2019)
iso_week_half(as.Date("2020-04-12"), 2021)
```

## Vectors

```{r}
dates <- seq(Sys.Date(), by = -1, length.out = 10)
tibble::tibble(date=dates, dow=lubridate::wday(dates, label=TRUE), week=iso_week_half(dates))
```

